\documentclass[10pt,letterpaper]{article}

\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage[paper=letterpaper,margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup {
  pdfcreator={Ivan Guerra},
  pdfproducer={Ivan Guerra},
  pdftitle={Ivan Eduardo Guerra - Resume},
  pdfauthor={Ivan Guerra},
  pdfsubject={Resume},
  colorlinks=true,
  linkcolor=NavyBlue,
  urlcolor=NavyBlue
}

\begin{document}
\newgeometry{top=0.25in, bottom=0.25in, right=0.4in, left=0.4in}

\hrule
\begin{center}
        \begin{LARGE}
                \textbf{Ivan Eduardo Guerra}
        \end{LARGE}
\end{center}
\hrule

\medskip

\begin{minipage}[t]{0.53\textwidth}
        \begin{flushleft}
                \textbf{Permanent Address:}\\
                800 Meyer Lane \#18\\
                Redondo Beach, CA 90278\\
                E-mail: \href{mailto:ivan.eduardo.guerra@gmail.com}{ivan.eduardo.guerra@gmail.com}
        \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.44\textwidth}
        \begin{flushright}
                \begin{flushleft}
                        \textbf{Contact Information:}\\
                        Mobile Phone \#: (580) 341-8882\\
                        Alternate E-mail: \href{mailto:Ivan.E.Guerra-1@ou.edu}{Ivan.E.Guerra-1@ou.edu}\\
                        \underline{\textbf{GitHub:} \url{www.github.com/ivan-guerra}}
                \end{flushleft}
        \end{flushright}
\end{minipage}

\smallskip

\begin{large}
        \textbf{Education}
\end{large}

\smallskip \hrule \smallskip

\begin{minipage}[t]{0.5\textwidth}
        \begin{flushleft}
                \textbf{University of Oklahoma: Norman, OK}\\
                \textbf{\textit{B.S. Computer Science}}

                \begin{itemize}[noitemsep,topsep=0pt]
                        \setlength\itemsep{-0.10em}
                        \item \textbf{3.96}/4.00 Cumulative GPA
                        \item Mathematics Minor
                        \item Spanish Minor (Bilingual)
                \end{itemize}

        \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.47\textwidth}
        \begin{flushright}
                \textbf{Fall 2013 - Spring 2017}

                \begin{itemize}[noitemsep,topsep=14pt]
                        \item Lean/6 Sigma Green Belt Certified
                        \item University of Oklahoma Honors College
                \end{itemize}

        \end{flushright}
\end{minipage}

\medskip

\begin{large}
        \textbf{Professional Experience}
\end{large}

\smallskip \hrule \smallskip

\begin{minipage}[t]{0.53\textwidth}
        \begin{flushleft}
                \textbf{Raytheon - Space and Airborne Systems}\\
                \textbf{\textit{Electro-Optic/Infra-Red Pod (EOIR) Software Engineer}}\\
        \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.44\textwidth}
        \begin{flushright}
                \textbf{June 2017 - Present}
        \end{flushright}
\end{minipage}

\begin{itemize}[noitemsep,topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item Increased EOIR C++ test coverage from 22\% to 35\% by integrating the gcov
              source code coverage tool into the EOIR build system.
        \item Discovered numerous memory and threading errors in the EOIR C++ codebase
              by using the Valgrind Memcheck/Helgrind tools, leading to an effort to correct
              the errors prior to proceeding with product development.
        \item Parallelized the EOIR software build on Windows and Linux by updating legacy Jenkins
              CI Java configuration scripts, causing a more than 30\% reduction in the job
              queue size.
\end{itemize}

\medskip

\begin{minipage}[t]{0.53\textwidth}
        \begin{flushleft}
                \textbf{ExxonMobil - Data and Information Systems}\\
                \textbf{\textit{Manufacturing and Supply Applications Engineer}}\\
        \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.44\textwidth}
        \begin{flushright}
                \textbf{May 2016 - August 2016}
        \end{flushright}
\end{minipage}

\begin{itemize}[noitemsep,topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item Automated the process of optimally loading chemical cargo aboard
              vessels by applying dynamic programming techniques, leading to a 20
              hours per week time savings.
        \item Reduced the frequency of chemical cargo contamination by implementing
              a Java user interface to assist engineers in accurately managing cargo data.
        \item Applied user-centered design techniques to create a software
              requirements document providing a base set of requirements for continued
              product development.
\end{itemize}

\medskip

\begin{minipage}[t]{0.53\textwidth}
        \begin{flushleft}
                \textbf{Northrop Grumman - B-2 Defense Management Systems}\\
                \textbf{\textit{B-2 Display Systems Software Engineer}}\\
        \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.44\textwidth}
        \begin{flushright}
                \textbf{January 2015 - August 2015}
        \end{flushright}
\end{minipage}

\begin{itemize}[noitemsep,topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item Discovered and removed software defects in the
              Platform Systems Tools C++ source code using the GNU Debugger and Valgrind
              Memcheck, saving software quality assurance engineers over 30 hours of
              testing.
        \item Increased Platform Systems Tool's C++ test coverage from 60\% to 68\% by
              implementing over 30 unit tests using the Google Test library.
        \item Improved the B-2 display system team's API documentation by writing C code
              snippets demonstrating the intended use and functionality of each method.
\end{itemize}

\medskip

\begin{large}
        \textbf{Technical Experience - Projects}
\end{large}

\smallskip \hrule \smallskip

\begin{itemize}[topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item \textbf{Atari Go} (2017). Command line implementation of the original Atari Go game supporting multiplayer and single player modes. C++, Doxygen
        \item \textbf{Simplex Solver} (2016). GUI-based linear programming problem solver capable of solving nonstandard LPPs and detecting infeasible/unbounded LPPs. Python
        \item \textbf{fdupe} (2016). Multithreaded file duplicate detection program implementing a thread-safe list and map. C, Doxygen
\end{itemize}

\medskip

\begin{large}
        \textbf{Additional Experience and Awards}
\end{large}

\smallskip \hrule \smallskip

\begin{itemize}[topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item \textbf{Teaching Assistant} (Spring 2017): Teaching assistant for a graduate course in cryptography; advised 33 students.
        \item \textbf{Hypercube Scholar Award}: Named a Hypercube Scholar for outstanding undergraduate research in computational biology.
\end{itemize}

\medskip

\begin{large}
        \textbf{Languages and Technologies}
\end{large}

\smallskip \hrule \smallskip

\begin{itemize}[topsep=0pt]
        \setlength\itemsep{-0.10em}
        \item Languages: C++ (proficient), C (proficient), Java (competent), Python (competent), Bash (competent)
        \item Testing Tools: Google Test, GNU Debugger, Valgrind Memcheck/Helgrind, Gcov
        \item Version Control Software: Git, Subversion
\end{itemize}

\end{document}